---
title: "Principle Component Analysis"
author: "Diren Kocakusak"
date: "17/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Libraries
```{r}
library(readr)
library(lm.beta)
library(pls)
library(psych)
library(ggbiplot)
library(ggplot2)
```

# Importing and Attaching the Linear Regression Model Dataset
```{r}
tts_lm <- read_csv("tts_lm.csv", col_types = cols(X1 = col_skip()))
attach(tts_lm)
```

## Linear Regression Model
```{r}
tts_lm.fit = lm(adoption_rate ~ . - zipcode, data = tts_lm)
summary(tts_lm.fit)
# Standardized Coefficients
std_tts_lm <- lm.beta(tts_lm.fit)
summary(std_tts_lm)
```

## Drop zipcode and DV and save a new dataframe
```{r}
pca.fit <- subset(tts_lm, select = -c(zipcode, adoption_rate))
```

### Save the Residuals
```{r}
tts_lm$residuals <- residuals(tts_lm.fit)
```

### Export the Residuals
```{r}
write.csv(tts_lm, file = "tts_lm_resid.csv")
```

# Principle Component Analysis
## Deciding the Number of Principle Components
```{r}
principal <- principal(pca.fit, nfactors = 5, rotate = "none", scores = TRUE)
principal
```

## Eigenvalues
```{r}
principal$values
```

## Principal Component Analysis with Varimax Rotation
```{r}
principal.varimax <- principal(pca.fit, nfactors = 5, rotate = "varimax", scores = T)
principal.varimax
```

### Principle Component Regression with Varimax Rotation
```{r}
tts_lm.principal.varimax = lm(tts_lm$adoption_rate ~ principal.varimax$scores[,1] + principal.varimax$scores[,2] + principal.varimax$scores[,3] + principal.varimax$scores[,4] + principal.varimax$scores[,5])
summary(tts_lm.principal.varimax)
# Standardized Coefficients
std_tts_lm.principal.varimax <- lm.beta(tts_lm.principal.varimax)
summary(std_tts_lm.principal.varimax)
```

#### Calculate AIC
```{r}
AIC(tts_lm.principal.varimax)
```
